Considering scale in multilayer animal social networks

### 2020-06-11 paper/manuscript.Rmd
reflow, tidy

### Network layer construction
<!--We generated a multilayer social network consisting `r DT[, uniqueN(get(idcol))]`
individual nodes and two aspects (season and land cover). Two season
elementary-layers (summer and winter) and three land cover elementary-layers
(forage, forest, and open) combined for a total of six layers. Single layers were
composed of individuals linked by social associations, for each season and land cover combination. Proximity-based social
network layers were generated using the R package `spatsoc` [@Robitaille_2019]
in `r version$version.string` [@R_Core_Team_2019].-->

We generated proximity-based social networks using the R package `spatsoc`
[@Robitaille_2019] in `r version$version.string` [@R_Core_Team_2019]. We assumed
individuals were associating if simultaneous GPS fixes were within the spatial
distance threshold of one another. Typically for ungulates and other gregarious
mammals, the ‘chain rule’ is used for group assignment [@Croft_2008]. For GPS
data, the chain rule is applied by assigning a group identifier to the union of
buffered GPS fixes at each time step. As such, individuals in a group are within
the spatial distance threshold of at least one other though not necessarily all
other individuals [@Robitaille_2019]. Group assignment based on the chain rule
has previously been applied to caribou using a temporal treshold of 5 minutes
and a spatial distance threshold of 50 m [@Peignier_2019; @Lesmerises_2018].

@@

We used a series of metrics to characterize the multilayer networks, focusing on
the role of individuals, importance of individual layers, and the similarity of
different layers. To measure the role of individuals, we calculated degree
centrality and graph strength. Degree centrality is the number of direct
connections an individual has to other individuals in a network layer. Graph
strength is the degree weighted by the strength of association, in this case
SRI, in each layer-specific season and land cover context. Extending degree
centrality, we calculated multidegree, the sum of degree centrality of
individuals across layers, and neighbourhood, the sum of unique neighbours to
each individual across layers [@Berlingerio_2012; @Kivela_2014]. We evaluated
the relevance and redundancy of layers by combining the multidegree and
neighbourhood to calculate layer relevance and connective redundancy. Layer
relevance is the proportion of neighbours present in each layer compared to the
neighbourhood for each individual and connective redundancy is the proportion of
neighbours repeated in multiple layers, and [@Berlingerio_2012]. Finally, we
calculated the similarity of layers between seasons, across land cover classes
(e.g. summer open compared to winter open) using the Pearson correlation
coefficient [@Brodka_2018]. Network metrics were calculated using the R packages
`igraph` [@Csardi_2006], `asnipe` [@Farine_2019] and `data.table` [@Dowle_2019].
<!-- add used spatsoc -->

>>>>

### Network layer construction
<!--We generated a multilayer social network consisting `r DT[, uniqueN(get(idcol))]`
individual nodes and two aspects (season and land cover). Two season
elementary-layers (summer and winter) and three land cover elementary-layers
(forage, forest, and open) combined for a total of six layers. Single layers were
composed of individuals linked by social associations, for each season and land cover combination.-->

We generated proximity-based social networks using the R package `spatsoc`
[@Robitaille_2019] in `r version$version.string` [@R_Core_Team_2019]. We assumed
individuals were associating if simultaneous GPS fixes were within the spatial
distance threshold of one another. Typically for ungulates and other gregarious
mammals, the ‘chain rule’ is used for group assignment [@Croft_2008]. For GPS
data, the chain rule is applied by assigning a group identifier to the union of
buffered GPS fixes at each time step. As such, individuals in a group are within
the spatial distance threshold of at least one other though not necessarily all
other individuals [@Robitaille_2019]. Group assignment based on the chain rule
has previously been applied to caribou using a temporal threshold of 5 minutes
and a spatial distance threshold of 50 m [@Peignier_2019; @Lesmerises_2018].

@@

We used a series of metrics to characterize the multilayer networks, focusing on
the role of individuals, importance of individual layers, and the similarity of
different layers. To measure the role of individuals, we calculated degree
centrality and graph strength. Degree centrality is the number of direct
connections an individual has to other individuals in a network layer. Graph
strength is the degree weighted by the strength of association, in this case
SRI, in each layer-specific season and land cover context. Extending degree
centrality, we calculated multidegree, the sum of degree centrality of
individuals across layers, and neighbourhood, the sum of unique neighbours to
each individual across layers [@Berlingerio_2012; @Kivela_2014]. We evaluated
the relevance and redundancy of layers by combining the multidegree and
neighbourhood to calculate layer relevance and connective redundancy. Layer
relevance is the proportion of neighbours present in each layer compared to the
neighbourhood for each individual and connective redundancy is the proportion of
neighbours repeated in multiple layers, and [@Berlingerio_2012]. Finally, we
calculated the similarity of layers between seasons, across land cover classes
(e.g. summer open compared to winter open) using the Pearson correlation
coefficient [@Brodka_2018]. Network metrics were calculated using the R packages
`igraph` [@Csardi_2006], `asnipe` [@Farine_2019], `spatsoc`
[@Robitaille_2019] and `data.table` [@Dowle_2019].
